%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\name{Jack Kosaian} % Your name
\address{\href{https://jackkosaian.github.io}{jackkosaian.github.io} \\ jkosaian@andrew.cmu.edu}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Carnegie Mellon University} \hfill {Aug. 2017 - Present} \\
Ph.D. in Computer Science \\
Advisor: Rashmi Vinayak

{\bf University of Michigan, Ann Arbor} \hfill {Sept. 2013 - Dec. 2016} \\ 
B.S.E. in Computer Science \& Engineering

\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Awards}
- NSF Graduate Research Fellowship (2017)\\
- Angell Scholar (2015)\\
- Branstrom Prize (2014)

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research}

\begin{rSubsection}{Software Systems Laboratory}{Jan. 2016 - April 2017}{Undergraduate Research Assistant}{Ann Arbor, MI}
\item Geo-distributed Analytics: Co-optimizing scheduling and routing of jobs across datacenters
\item EC-Cache: Using erasure coding to mitigate load imbalance and reduce read latencies for cluster storage
\end{rSubsection}

\begin{rSubsection}{Laboratory for Interactive Visualization in Engineering}{June 2014 - April 2015}{Undergraduate Research Assistant}{Ann Arbor, MI}
\item SmartDig: Computer vision techniques to perform automatic, accurate pose-estimation of excavators
\end{rSubsection}

\begin{rSubsection}{S.M. Wu Manufacturing Research Center}{Jan. 2014 - Dec. 2014}{Undergraduate Research Assistant}{Ann Arbor, MI}
\item Intelligent Eye Model: Anatomically accurate model of they eye used to train ophthalmology residents
\end{rSubsection}
\end{rSection}

\begin{rSection}{Publications}
\bibliographystyle{plain}
\bibliography{cv}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Industry}

\begin{rSubsection}{Google}{May 2017 - July 2017}{Software Engineering
Intern}{Seattle, WA}
\item BigQuery
\end{rSubsection}

\begin{rSubsection}{Google}{May 2016 - Aug. 2016}{Software Engineering
Intern}{Mountain View, CA}
\item Cloud Technical Infrastructure: Kernel Virtualization
\end{rSubsection}

\begin{rSubsection}{Epic Systems Corporation}{May 2015 - Aug. 2015}{Software
Development Intern}{Verona, WI}
\item InPatient: Scoring System Analysis and Visualization
\end{rSubsection}
\end{rSection}

\begin{rSection}{Teaching}
- EECS 370: Introduction to Computer Organization (F15, W16)
\end{rSection}

\end{document}
